\documentclass{ximera}

\title{Master Test Activity}

\begin{document}

\begin{abstract}
  One test to rule them all.
\end{abstract}

\maketitle

Some text before my problems.

\begin{problem}
	Q1
	\begin{parts}[hide]
		\item Q1a
		\item Q1b
	\end{parts}
\end{problem}

\begin{question}
	Q2
\end{question}

\begin{question}
	Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. Q3 is a really long one. 
	\begin{hints}
		\item A hint for Q3.
		\item A really long hint for Q3. A really long hint for Q3. A really long hint for Q3. A really long hint for Q3. A really long hint for Q3. A really long hint for Q3. A really long hint for Q3. A really long hint for Q3. A really long hint for Q3.
		\begin{hints}
			\item A hint for that really long hint for Q3.
		\end{hints}
		\begin{hints}
			\item Another hint for that really long hint.
		\end{hints}
	\end{hints}
	\begin{parts}
		\item Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. 
		\item Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. Q3 has really long parts. 
	\end{parts}
\end{question}

\begin{question}
	Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. 
	
	Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. Q4 is another long one. 
\end{question}

\begin{exploration}
	Q5
\end{exploration}

Some text after my problems.

Some more text after my problems.


\end{document}
